Taking uncertainty in word embedding bias estimation seriously: a bayesian approach

### 2022-07-28 paperDraft/paperDraft4.Rmd
Updates chapters alicja

>>>>

### What is Bayesian statistics?

Bayesian statistics is a theory which enables one to assign epistemological uncertainty with the use of probability. It is a system that allows to express a degree of belief in a certain event. Bayesian methods use existing prior beliefs together with real data to receive posterior beliefs.
Bayesian inference together with probability tools may be used to quantify the uncertainty in the inferences.

### How does it differ from the classical statistics?

One could ask what is the difference between Bayesian statistics and the classical, frequentist approach. Broadly speaking the Frequentist statistics looks, as the name suggests, at the frequency of an event in a long run and based on that assigns its probability. In Bayesian statistics the approach is more epistemological as one may include his/her prior beliefs on the likelihood of an event and update it accordingly to the available data which results in the posterior probability of an event. What is more in a classical approach, the parameters are fixed whereas in Bayesian statistics the parameters are assumed to be random variables to which one assigns a probability distribution. In contrast with CIs, the posterior distributions (and their highest posterior density intervals HPDIs, the narrowest intervals containing a certain ratio of the area under the curve) are easily interpretable and have direct relevance for the question at hand.

### How does the Bayesian model work?

Referring to the \textit{Statistical rethinking} one may distinguish three steps that are necessary to design Bayesian model:
1. Data story: Think about the narrative on how the data can emerge. 
2. Update: Let the model learn from the data.
3. Evaluate: Verify whether it is a good representation of the phenomenon.

A Bayesian model consists of the variables and the distributions that define these variables. The priors that one assigns provide the likelihood of each parameter before any data has been seen. Then using real data one may apply numerical techniques like Markov chain Monte Carlo to calculate the posterior distribution.

### Interpreting model's results

The standard output from the model's learning may contain the following pieces of information.

WAIC -

### What are hierarchical models?

Hierarchical models are also known as multilevel models, random effects, varying effects, or mixed effects models. In \textit{Statistical rethinking} one may read that the central device of the multilevel models is to learn the strength of the prior from the data itself. Multilevel models may be regarded as adaptive regularization, meaning that the model tunes itself to get the most optimal skepticism. It is worth mentioning that with these types of models adding more parameters can sometimes lead to the effect where effective number of parameters (the penalty term in WAIC) is actually reduced. The overfitting may be more dependent on how the parameters are related to one another than with how many parameters one inputs into the model.

### Coding example from our model

To build a model one may use original \textit{Stan} which is a state-of-the-art platform for statistical modeling and high-performance statistical computation (https://mc-stan.org/). The simpler option is to use \textit{Rethinking} package from the \textit{Statistical rethinking} course. With one of the functions \textit{ulam} one may build RStan models from the formulas in an easy manner.

Explain the model?

```{r, eval=FALSE, echo=TRUE}
buildModel <- function(dataset){
  options(buildtools.check =
  function(action) TRUE )

  modelResult <- ulam(
    alist(
      distance ~ dnorm(mu,sigma),
      mu <- d[pwi] * different
      + a[pwi] * associated
      + h[pwi] * human
      + n[pwi] * none,

      d[pwi] ~ dnorm(dbar, dsigmabar),
      a[pwi] ~ dnorm(abar, asigmabar),
      h[pwi] ~ dnorm(hbar, hsigmabar),
      n[pwi] ~ dnorm(nbar, nsigmabar),

      dbar ~ dnorm(1,.3),
      abar ~ dnorm(1,.3),
      hbar ~ dnorm(1,.3),
      nbar ~ dnorm(1,.3),
      dsigmabar ~ dexp(2),
      asigmabar ~ dexp(2),
      hsigmabar ~ dexp(2),
      nsigmabar ~ dexp(2),
      sigma <- s[connection],
      s[connection] ~  dexp(2)
    ),

    data = dataset, chains=2 ,
    iter=8000 , warmup=1000,
    log_lik = TRUE, cores = 4
  )
}
```

### Limitations

Each method has its own limitations and Bayesian statistics is no exception. One may think about a few limitations with this approach. One of them is that there is no final and correct way to choose a prior. At the same time prior beliefs can be explicitly stated, debated, or often found in previous research which may give good justification for a given set of priors. Finally, Bayesian method may be computationally expensive which may be a limiting factor when considering to use it in a more real-time environment.

### 2022-07-28 paperDraft/paperDraft4.tex
Updates chapters alicja

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames,enabledeprecatedfontcommands, twocolumn]{scrartcl}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Taking uncertainty in word embedding bias estimation seriously: a bayesian approach},
  pdfauthor={Alicja Dobrzeniecka and Rafal Urbaniak},
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
%\documentclass{article}

@@

\hypertarget{what-is-bias}{%
\subsection{What is bias?}\label{what-is-bias}}

\hypertarget{word-embeddings}{%
\subsection{Word embeddings}\label{word-embeddings}}

Modern Natural Language Processing (NLP) models are used to complete
various tasks such as providing email filters, smart assistants, search
results, language translations, text analytics and so on. All of them
need as an input words represented by means of numbers which is
accomplished with word embeddings, in which particular lexical units are
repesented as vectors of real numbers. It has been suggested {[}1--6{]}
that in the learning process such models can learn implicit biases that
reflect harmful stereotypical thinking. A large chunk of the literature
on the topic focuses on the geometry of the learnt word embeddings; in
particular, unusually low (cosine) proximity of words belonging,
intuitively, to a stereotype, is taken as a sign that this stereotype
has been built into a given embedding. This methodology will be in the
focus of our paper.

\hypertarget{semantical-interpretation}{%
\subsection{Semantical interpretation}\label{semantical-interpretation}}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames,enabledeprecatedfontcommands, twocolumn]{scrartcl}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Taking uncertainty in word embedding bias estimation seriously: a bayesian approach},
  pdfauthor={Alicja Dobrzeniecka and Rafal Urbaniak},
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
%\documentclass{article}

@@

\hypertarget{word-embeddings-and-their-bias}{%
\subsection{Word embeddings and their
bias}\label{word-embeddings-and-their-bias}}

\begin{itemize}
\tightlist
\item
  akapit filozoficzny, z odniesieniem do value free
\end{itemize}

Modern Natural Language Processing (NLP) models are used to complete
various tasks such as providing email filters, smart assistants, search
results, language translations, text analytics and so on. All of them
need as an input words represented by means of numbers which is
accomplished with word embeddings, in which particular lexical units are
represented as vectors of real numbers.

\begin{itemize}
\item
  troche o tym jak sa skonstruowane (optimizing for co-ocurrence
  frequency)
\item
  przejrzec jak to jest wprowadzane w kilku innych artykulach, zwl. fair
  is better than sensational
\item
  troche wiecej o tej konstrukcji i intuicji semantycznych, ale to nie
  super dobry pomysl
\item
  undesirable bias with respect to a certain groups words if
  stereotypically connected words (for stereotypes that we don't want to
  be used or relied on in downstream tasks) are systematically closer to
  each other. + EXAMPLES
\end{itemize}

It has been suggested {[}1--6{]} that in the learning process such
models can learn implicit biases that reflect harmful stereotypical
thinking. A large chunk of the literature on the topic focuses on the
geometry of the learnt word embeddings; in particular, unusually low
(cosine) proximity of words belonging, intuitively, to a stereotype, is
taken as a sign that this stereotype has been built into a given
embedding. This methodology will be in the focus of our paper.

@@

\hypertarget{what-is-bayesian-statistics}{%
\subsubsection{What is Bayesian
statistics?}\label{what-is-bayesian-statistics}}

Bayesian statistics is a theory which enables one to assign
epistemological uncertainty with the use of probability. It is a system
that allows to express a degree of belief in a certain event. Bayesian
methods use existing prior beliefs together with real data to receive
posterior beliefs. Bayesian inference together with probability tools
may be used to quantify the uncertainty in the inferences.

\hypertarget{how-does-it-differ-from-the-classical-statistics}{%
\subsubsection{How does it differ from the classical
statistics?}\label{how-does-it-differ-from-the-classical-statistics}}

One could ask what is the difference between Bayesian statistics and the
classical, frequentist approach. Broadly speaking the Frequentist
statistics looks, as the name suggests, at the frequency of an event in
a long run and based on that assigns its probability. In Bayesian
statistics the approach is more epistemological as one may include
his/her prior beliefs on the likelihood of an event and update it
accordingly to the available data which results in the posterior
probability of an event. What is more in a classical approach, the
parameters are fixed whereas in Bayesian statistics the parameters are
assumed to be random variables to which one assigns a probability
distribution. In contrast with CIs, the posterior distributions (and
their highest posterior density intervals HPDIs, the narrowest intervals
containing a certain ratio of the area under the curve) are easily
interpretable and have direct relevance for the question at hand.

\hypertarget{how-does-the-bayesian-model-work}{%
\subsubsection{How does the Bayesian model
work?}\label{how-does-the-bayesian-model-work}}

Referring to the \textit{Statistical rethinking} one may distinguish
three steps that are necessary to design Bayesian model: 1. Data story:
Think about the narrative on how the data can emerge. 2. Update: Let the
model learn from the data. 3. Evaluate: Verify whether it is a good
representation of the phenomenon.

A Bayesian model consists of the variables and the distributions that
define these variables. The priors that one assigns provide the
likelihood of each parameter before any data has been seen. Then using
real data one may apply numerical techniques like Markov chain Monte
Carlo to calculate the posterior distribution.

\hypertarget{interpreting-models-results}{%
\subsubsection{Interpreting model's
results}\label{interpreting-models-results}}

The standard output from the model's learning may contain the following
pieces of information.

WAIC -

\hypertarget{what-are-hierarchical-models}{%
\subsubsection{What are hierarchical
models?}\label{what-are-hierarchical-models}}

Hierarchical models are also known as multilevel models, random effects,
varying effects, or mixed effects models. In
\textit{Statistical rethinking} one may read that the central device of
the multilevel models is to learn the strength of the prior from the
data itself. Multilevel models may be regarded as adaptive
regularization, meaning that the model tunes itself to get the most
optimal skepticism. It is worth mentioning that with these types of
models adding more parameters can sometimes lead to the effect where
effective number of parameters (the penalty term in WAIC) is actually
reduced. The overfitting may be more dependent on how the parameters are
related to one another than with how many parameters one inputs into the
model.

\hypertarget{coding-example-from-our-model}{%
\subsubsection{Coding example from our
model}\label{coding-example-from-our-model}}

To build a model one may use original \textit{Stan} which is a
state-of-the-art platform for statistical modeling and high-performance
statistical computation (\url{https://mc-stan.org/}). The simpler option
is to use \textit{Rethinking} package from the
\textit{Statistical rethinking} course. With one of the functions
\textit{ulam} one may build RStan models from the formulas in an easy
manner.

Explain the model?

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{buildModel }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(dataset)\{}
  \FunctionTok{options}\NormalTok{(}\AttributeTok{buildtools.check =}
  \ControlFlowTok{function}\NormalTok{(action) }\ConstantTok{TRUE}\NormalTok{ )}

\NormalTok{  modelResult }\OtherTok{\textless{}{-}} \FunctionTok{ulam}\NormalTok{(}
    \FunctionTok{alist}\NormalTok{(}
\NormalTok{      distance }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(mu,sigma),}
\NormalTok{      mu }\OtherTok{\textless{}{-}}\NormalTok{ d[pwi] }\SpecialCharTok{*}\NormalTok{ different}
      \SpecialCharTok{+}\NormalTok{ a[pwi] }\SpecialCharTok{*}\NormalTok{ associated}
      \SpecialCharTok{+}\NormalTok{ h[pwi] }\SpecialCharTok{*}\NormalTok{ human}
      \SpecialCharTok{+}\NormalTok{ n[pwi] }\SpecialCharTok{*}\NormalTok{ none,}

\NormalTok{      d[pwi] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(dbar, dsigmabar),}
\NormalTok{      a[pwi] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(abar, asigmabar),}
\NormalTok{      h[pwi] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(hbar, hsigmabar),}
\NormalTok{      n[pwi] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(nbar, nsigmabar),}

\NormalTok{      dbar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
\NormalTok{      abar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
\NormalTok{      hbar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
\NormalTok{      nbar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
\NormalTok{      dsigmabar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{2}\NormalTok{),}
\NormalTok{      asigmabar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{2}\NormalTok{),}
\NormalTok{      hsigmabar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{2}\NormalTok{),}
\NormalTok{      nsigmabar }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{2}\NormalTok{),}
\NormalTok{      sigma }\OtherTok{\textless{}{-}}\NormalTok{ s[connection],}
\NormalTok{      s[connection] }\SpecialCharTok{\textasciitilde{}}  \FunctionTok{dexp}\NormalTok{(}\DecValTok{2}\NormalTok{)}
\NormalTok{    ),}

    \AttributeTok{data =}\NormalTok{ dataset, }\AttributeTok{chains=}\DecValTok{2}\NormalTok{ ,}
    \AttributeTok{iter=}\DecValTok{8000}\NormalTok{ , }\AttributeTok{warmup=}\DecValTok{1000}\NormalTok{,}
    \AttributeTok{log\_lik =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{cores =} \DecValTok{4}
\NormalTok{  )}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{limitations}{%
\subsubsection{Limitations}\label{limitations}}

Each method has its own limitations and Bayesian statistics is no
exception. One may think about a few limitations with this approach. One
of them is that there is no final and correct way to choose a prior. At
the same time prior beliefs can be explicitly stated, debated, or often
found in previous research which may give good justification for a given
set of priors. Finally, Bayesian method may be computationally expensive
which may be a limiting factor when considering to use it in a more
real-time environment.
